%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {M.S. in High Performance Computing} % Degree
    {UNILU(Université du Luxembourg)} % Institution
    {Belvaux, Luxembourg} % Location
    {Sep. 2025 - May 2026} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Currently in my firest semester under the program EUMaster4HPC for a double degree.}
        \item {I will spend my first year on Université du Luxembourg, and the second year in Sofia University St. Kliment Ohridski. Together with a summer school in the July 2026.}
      \end{cvitems}
    }

  \cventry
    {B.S. in Computer Science} % Degree
    {GT(Georgia Insitute of Technology)} % Institution
    {Georgia, USA} % Location
    {Aug. 2023 - May. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Comprehensive knowledge of computer systems architecture and implementation with focus on distributed computing environments.}
        \item {Proficient in systems-level programming and designing robust networked applications for modern computing infrastructures.}
        \item {Relevant coursework: Advanced Operating Systems, Embedded Systems, Database implementation and Cyber Security.}
        \item {GPA: 4/4}
      \end{cvitems}
    }
  \cventry
    {B.S. in Computer Engineering} % Degree
    {UC3M(Universidad Carlos III de Madrid)} % Institution
    {Madrid, Spain} % Location
    {Sep. 2020 - Jun. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Solid foundation in mathematics and statistics; as well Artificial Intelligence, Software Engineering, Cyber Security, among many others.}
        \item {Completed capstone project: Developed project HERMES (High Performance Enginer for Routing and Mirroring Encrypted Streams) in C++, a proxy for load-balancing millions of connections within an internal network.}
        \item {Courses include: Operating Systems, Networks, Distributed Systems, Computer Architecture, Software Engineering, Machine Learning and Cryptography.}
        \item {GPA: 9.1/10}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
