%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
    {\href{https://github.com/nekronos-gh/rule110}{github.com/nekronos-gh/rule110}}
    {Rule110 Fast}
    {}
    {}
    {
      \begin{cvitems}
        \item {Optimized Rule 110 simulation using AVX2 SIMD intrinsics.} 
        \item {Maximised memory throughput via memory alignment and OpenMP multi-threading.}
        \item {Utilized hardware directives and C++23 features for efficient state analysis.}
      \end{cvitems}
    }

  %---------------------------------------------------------

  \cventry
    {\href{https://github.com/nekronos-gh/TinyFile}{github.com/nekronos-gh/TinyFile}}
    {TinyFile}
    {}
    {}
    {
      \begin{cvitems}
        \item {Developed a file compression service using a hybrid IPC architecture combining POSIX Message Queues control signals and Shared Memory for data transfer.}
        \item {Engineered a state-machine based Ring Buffer to manage concurrent data chunks, utilizing zero-copy memory access between the client library and daemon service.}
      \end{cvitems}
    }

  %---------------------------------------------------------

  \cventry
    {\href{https://github.com/nekronos-gh/pbft-cpp}{github.com/nekronos-gh/pbft-cpp}}
    {PBFT}
    {}
    {}
    {
      \begin{cvitems}
        \item {Implemented Practical Byzantine Fatult Tolerance (PBFT) proctocol in C++ using Salticidae for network connection, together with Prometheus and Grafana for monitoring.}
        \item {Three phase conensus protcol (pre-prepare, prepare and commit phases), that handles primary errors through view changes.}
        \item {Included state checkpointing for garbage collection and state synchronization.}
      \end{cvitems}
    }

\end{cventries}
