

\section{Professional Experience}

\subsection{Samsung Electronics (Zhilabs)}
\textbf{Role:} Software Engineer

\begin{itemize}
    \item \textbf{Recursive Descent Binary Parser for Network Traces}
    \begin{itemize}
        \item \textbf{Timeline:} June - July 2023
        \item \textbf{Contributions:}
        \begin{itemize}
            \item Developed a fully functional recursive descent binary parser to efficiently access and collect network error data from traces.
            \item Enhanced system performance by providing quick and reliable data extraction, critical for troubleshooting and network optimization.
        \end{itemize}
    \end{itemize}

    \item \textbf{Parallel Network Traffic Simulation}
    \begin{itemize}
        \item \textbf{Timeline:} June - July 2023
        \item \textbf{Contributions:}
        \begin{itemize}
            \item Upgraded an existing network traffic simulator from sequential execution to parallel simulation across multiple antennas.
            \item Significantly improved the simulator’s performance, enabling more accurate and scalable testing of network scenarios.
        \end{itemize}
    \end{itemize}

    \item \textbf{High-Performance Network Trace Proxy}
    \begin{itemize}
        \item \textbf{Timeline:} January - March 2024
        \item \textbf{Contributions:}
        \begin{itemize}
            \item Designed and implemented a high-performance proxy for network traces, built from the ground up.
            \item Achieved a breakthrough throughput of 86 Gb/s for unencrypted packet forwarding, surpassing all performance expectations.
            \item Presented the project as my Bachelor's Thesis in Summer 2024, marking the capstone of my undergraduate degree.
        \end{itemize}
    \end{itemize}
    
    \item \textbf{RAN (Radio Access Network) Assistant}
    \begin{itemize}
        \item \textbf{Timeline:} July - October 2024
        \item \textbf{Contributions:}
        \begin{itemize}
            \item Engaged from the Proof of Concept stage, ensuring robust research and architecture design.
            \item Using a blend of LLM, NLP, ML, and traditional heuristics to build a solution.
            \item Implemented a multi-agent system capable of: understanding natural language, learning from internal telco documentation, and interacting directly with Samsung's network management tools.
            \item The most relevant features include: Telco Question Answering, Anomaly Detection, Root Cause Analysis, and Solution Proposal. 
        \end{itemize}
    \end{itemize}
\end{itemize}

\subsection{Ericsson}
\textbf{Role:} Software Developer
\begin{itemize}
    \item \textbf{Research and Development for 5G Core}
    \begin{itemize}
        \item \textbf{Timeline:} Ongoing since December 2024
        \item \textbf{Contributions:}
        \begin{itemize}
            \item Member of a small team dedicated to User Plane Analytics and Optimization of the core network behind 5G technology.
            \item My role consists of developing new features (e.g. antenna geo-redundancy algorithms), creating network improvements (e.g. reducing contention in a multi-thread process), and fixing trouble reports (e.g. solving a segment violation error).
        \end{itemize}
    \end{itemize}
\end{itemize}
\hfill

